\cvsection{Research and Creative Scholarship}

  %\faTrophy
  %\faCertificate

  \cvsubsection{Peer-Reviewed Conference Presentations}

    \begin{cvpublications}
      \cvpublication%
        {C7.}%
        {\href{https://doi.org/10.1145/3526113.3545642}{AirLogic: Embedding Pneumatic Computation and I/O in 3D Models to Fabricate Electronics-Free Interactive Objects}}%
        {\textbf{Carlos E. Tejada}, Valkyrie Savage, Mengyu Zhong, Raf Ramakers, Daniel Ashbrook, Hyunyoung Kim}
        {To appear in 35th Annual ACM Symposium on User Interface Software and Technology}
        {Bend, Oregon, 2022, 10 pages. (25\% acceptance rate)}
      \cvpublication%
        {C6.}%
        {\href{https://doi.org/10.1145/3490149.3501314}{ClipWidgets: 3D-printed Modular Tangible UI Extensions for Smartphones}}%
        {Aaron Visschedijk, Hyunyoung Kim, \textbf{Carlos E. Tejada}, and Daniel Ashbrook}%
        {Sixteenth International Conference on Tangible, Embedded, and Embodied Interaction (TEI)}
        {Daejeon, Korea, 2022, 8 pages. (29\% acceptance rate)}
      \cvpublication%
        {C5.}%
        {\href{https://doi.org/10.1145/3313831.3376136}{MorpheesPlug: A Toolkit for Prototyping Shape-Changing Interfaces}}%
        {Hyunyoung Kim, Aluna Everitt, \textbf{Carlos E. Tejada}, Mengyu Zhong, and Daniel Ashbrook}%
        {Proceedings of the 2021 CHI Conference on Human Factors in Computing Systems (CHI)}%
        {Yokohama, Japan, 2021, 10 pages. (23\% acceptance rate)}
      \cvpublication%
        {C4.}%
        {\href{https://doi.org/10.1145/3313831.3376136}{AirTouch: 3D-printed Touch-Sensitive Objects Using Pneumatic Sensing}}%
        {\textbf{Carlos E. Tejada}, Raf Ramakers, Sebastian Boring, and Daniel Ashbrook}%
        {Proceedings of the 2020 CHI Conference on Human Factors in Computing Systems (CHI)}%
        {Honolulu, Hawaii, USA, 2020, 8 pages. (24.3\% acceptance rate)}
      \cvpublication%
        {C3.}
        {\href{https://doi.org/10.1145/3343055.3359712}{EchoTube: Robust Touch Sensing along Flexible Tubes using Waveguided Ultrasound}}%
        {\textbf{Carlos E. Tejada}, Jess McIntosh, Klæs Alexander Bergen, Sebastian Boring, Daniel Ashbrook, Asier Marzo}%
        {Proceedings of ACM Interna- tional Conference on Interactive Surfaces and Spaces (ISS)}%
        {Daejeon, Korea, 2019, 9 pages (30.6\% acceptance rate). \bf Honorable Mention Award}
      \cvpublication%
        {C2.}%
        {\href{https://doi.org/10.20380/GI2018.18}{Blowhole: Blowing-Activated Tags for Interactive 3D-Printed Models}}%
        {\textbf{Carlos E. Tejada}, Osamu Fujimoto, Zhiyuan Li. Daniel Ashbrook}%
        {Proceedings of the 44th Graphics Interface Conference (GI’18)}%
        {Toronto, ON, 2018, 6 pages (43\% acceptance rate)}
      \cvpublication%
        {C1.}%
        {\href{https://doi.org/10.1145/2935334.2935389}{Bitey: An Exploration of Tooth Click Gestures for Hands-Free User Interface Control}}%
        {Daniel Ashbrook, \textbf{Carlos E. Tejada}, Dhwanit Mehta, Anthony Jiminez, Goudam Muralitharam, Sangeeta Gajendra, Ross Tallents.}%
        {ACM 18th International Conference on Human-Computer Interaction with Mobile Devices and Services (MobileHCI)}%
        {Florence, Italy, 2016, 12 pages (23.9\% acceptance rate)}
    \end{cvpublications}

  \cvsubsection{Peer-Reviewed Doctoral Consortium}
    \begin{cvpublications}
      \cvpublication%
        {DC1.}%
        {\href{https://doi.org/10.1145/3334480.3375025}{Print-and-Play: 3D-printed Interactive Objects Without Assembly or Calibration}}%
        {\textbf{Carlos E. Tejada}}%
        {Extended Abstracts of the 2020 CHI Conference on Human Factors in Computing Systems (CHI EA ’20)}%
        {Honolulu, Hawaii, USA, 2020, 6 pages}
    \end{cvpublications}

  \cvsubsection{Peer-Reviewed Conference Special Interest Groups Proposals}
    \begin{cvpublications}
      \cvpublication%
        {SIG1.}%
        {\href{https://doi.org/10.1145/3334480.3381055}{Fostering HCI Research in, by, and for Latin America}}%
        {Adriana Alvarado Garcia, Karla Badillo-Urquiola, Mayra D. Barrera Machuca, Franceli L. Cibrian, Marianela Ciolfi Felice, Laura S. Gaytán-Lugo, Diego Gómez-Zará, Carla F. Griggio, Monica Perusquia-Hernandez, Soraia Silva-Prietch, \textbf{Carlos E. Tejada}, and Marisol Wong-Villacres}%
        {Extended Abstracts of the 2020 CHI Conference on Human Factors in Computing Systems (CHI EA ’20)}%
        {Honolulu, Hawaii, USA, 2020, 4 pages}
    \end{cvpublications}
%\begin{cvpublications}
%\cvpublication{<ID>}{<title>}{<authors>}{<venue>}
%\end{cvpublications}
