\cvsection{Education}

\begin{cventries}

  \cventry
    {Ph.D. in Computer Science / Human-Computer Interaction, focused on digital fabrication}
    {University of Copenhagen}
    {Copenhagen, Denmark}
    {2018 -- June 2021}
    {
      \begin{cvitems}
        \item Thesis title: \emph{Print-and-Play Fabrication}. Enabling the
          construction of interactive objects using pneumatic and acoustic
          techniques.
        \item Selected publications:
        \item \hspace{1em} Blowhole: Blowing-Activated Tags for Interactive 3D-Printed Models.
        \item \hspace{1em} EchoTube: Modular and Robust Press Sensing along Flexible Tubes using Waveguided Ultrasound.
        \item \hspace{1em} AirTouch: 3D-printed Touch-Sensitive Objects Using Pneumatic Sensing.
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Ph.D. in Computer Science}
    {Rochester Institute of Technology}
    {Rochester, New York, USA}
    {2017 -- 2018}
    {
      \begin{cvitems}
        \item Transferred to the University of Copenhagen.
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {M.Sc. in Information Science}
    {Rochester Institute of Technology}
    {Rochester, New York, USA}
    {2014 -- 2016}
    {
      \begin{cvitems}
        \item Special focus on machine learning and database management.
        \item Thesis title: \emph{Knock-on-Wood}
        \item \hspace{1em} Explored the use of machine learning and acoustic
          signal processing to identify physical materials as part of a digital
          fabrication pipeline.
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {B.Sc. in Systems Engineering}
    {Pontificia Universidad Cat\'olica Madre y Maestra}
    {Santiago, Dominican Republic}
    {2008 -- 2013}
    {
      \begin{cvitems}
        \item Special focus on information retrieval and database management.
        \item Thesis title: \emph{Solve-for-X}
        \item \hspace{1em} Developed a mobile and web application using
          computer vision and linear algebra that allows users to solve
          mathematical equations by taking a picture with their phones or
          computers.
      \end{cvitems}
    }

\end{cventries}
