
\cvsection{Employment}

\begin{cventries}
  \cventry
    {Postdoctoral Researcher}
    {Aarhus University}
    {Aarhus, Denmark}
    {June 2023 -- Present}
    {
      \begin{cvitems}
        \item Explored the use of generative artificial intelligence for computer-aided design (CAD).
        \item Created predictive models for time-series data to translate
        readings from 3D-printed sensors into human-readable information.
        \item Explored the creation of intra-buccal sensors for hands-free
        device use.
      \end{cvitems}
      \vspace{1em}
    }
  \cventry
    {Data Consultant}
    {Netcompany A/S}
    {Copenhagen, Denmark}
    {2021 -- 2023}
    {
      \begin{cvitems}
        \item Designed, developed and deployed a natural language processing and
        machine learning architecture to extract meaning from unstructured text,
        and classify document types based on their content using Python's data
        science ecosystem (i.e., Numpy, Scikit-learn, Pandas, Tensorflow).
        \item Designed, developed and deployed an ETL process for managing,
        transforming, aggergating and stardardizing of billions of geo-spatial
        data points using Python, SQL and Azure technologies.
        \item Contributed to the creation of a series of dashboards and
        visualization tools for quantitative and geo-spatial data using PowerBI.
        \item Created a natural language processing pipeline to extract meaning from digital correspondence in four different languages.
        \item Developed multiple predictive models for the classification and
        sorting of digital correspondence based on its contents.
        \item Implemented a predictive model selection pipeline for determining
        the best machine learning model algorithm and their specific parameters,
        depending on the incoming data.
      \end{cvitems}
      \vspace{1em}
    }
    
  \cventry
    {Ph.D. Fellow}
    {University of Copenhagen}
    {Copenhagen, Denmark}
    {2018 -- 2021}
    {
      \begin{cvitems}
        \item Explored and developed a variety of techniques to fabricate
        tangible, interactive devices using off-the-shelf equipment and
        materials.
        \item Developed a series of predictive machine learning models that
        translated raw sensor data into actionable information.
        \item Extensive use of the Python data science suite (e.g., Numpy,
        Scikit-learn, Pandas, PyTorch) to create custom predictive models for
        identifying interactions on tangible devices.
        \item Authored and published academic papers in top-tier conferences for
        Human-Computer Interaction.
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Graduate Research Assistant}
    {Rochester Institute of Technology}
    {Rochester, New York, USA}
    {2014 -- 2018}
    {
      \begin{cvitems}
        \item Developed a series of acoustic signal processing pipelines to
        extract significant features from recordings (e.g., frequency
        information, zero-crossing rate, etc.).
        \item Created multiple predictive machine learning models for novel
        wearable (i.e., hands-free device control using body movements)
        and activity recognition (i.e., detecting the status of objects and
        appliances based on their acoustic signatures) devices.
      \end{cvitems}
    }

  \cventry
    {Senior Software Developer}
    {Tous Software Corp.}
    {Miramar, Florida, USA}
    {2012 -- 2014}
    {
      \begin{cvitems}
        \item Managed a team developers in creating a new reporting portal for
          customers using Java, PHP, and Go.
        \item Interfaced between clients and developer team to effectively
          implement the requirements.
      \end{cvitems}
    }

\end{cventries}
